---
title: 'Hwk 2 Question 6: Part a and b'
output: html_notebook
---
Student: Jonathan Herrera <br/>
Course: Deep Learning CAP6619 <br/>
Fall 2018
```{r}
library(pixmap)
library(gdata)
library(plyr)
left1<-read.pnm(file="face/left1.pgm")
```
```{r}
plot(left1)
```

```{r}
left1.matrix<-left1@grey
left1
```
```{r}
left1.vector<-unmatrix(left1.matrix,byrow=T)
left1.frame<-data.frame(left1.vector)
left1.frame
```

```{r}
dim(left1.frame)
```

```{r}
loadImages <- function(pathName,fileNames, clasLabel) {
files<-list.files(path=pathName,pattern=fileNames,all.files=T,full.name=T,no..=T)
list_of_images=lapply(files,read.pnm)
plot(list_of_images[[1]])
n.images<-length(list_of_images)
image.matrix<-list_of_images[[1]]@grey
image.vector<-unmatrix(image.matrix,byrow=T)
for(ii in 2:n.images)
{
 i.matrix<-list_of_images[[ii]]@grey
 i.vector<-unmatrix(i.matrix,byrow=T)
 image.vector<-rbind(image.vector,i.vector)
}
image.frame<-data.frame(image.vector)
n.rows<-nrow(image.frame)
class1.label<-rep(clasLabel,n.rows)
image.frame<-cbind(image.frame,class1.label)
return (image.frame)
}
```

```{r}
left.frame <- loadImages("face","left*.*",1)
```
Show right turn face

```{r}
left.frame
```

```{r}
right.frame <- loadImages("face","right*.*",-1)
```
Show left turn face.
```{r}
right.frame
```

```{r}
total.frame<-rbind(left.frame,right.frame)
dim(total.frame)
```

```{r}
train.index<-sample(nrow(total.frame),nrow(total.frame)*0.4)
training.set<-total.frame[train.index,]
training.set
```
training set

```{r}
test.set<-total.frame[-train.index,]
test.set
```
Test set

```{r}
library(neuralnet)
myform <- as.formula(paste('class1.label ~ ',paste(names(training.set[!names(training.set) %in% 'class1.label']), collapse = ' + ')))
face.3.classifier <- neuralnet(myform, training.set, hidden = 3, rep=100, linear.output = FALSE, threshold = 0.1)
summary(face.3.classifier)
```
Model for 3 hidden nodes
```{r}
class.index<-length(test.set)
face.prediction<-compute(face.3.classifier,test.set[,-class.index])
face.prediction$net.result
```
Prediction for 3 hidden nodes
```{r}
classifications<-ifelse(face.prediction$net.result>0.5,1,-1)
classifications
```
Classification for 3 hidden nodes
```{r}
table(test.set[,class.index],classifications)
```
Classification accuracy table for 3 hidden nodes

```{r}
library(neuralnet)
myform <- as.formula(paste('class1.label ~ ',paste(names(training.set[!names(training.set) %in% 'class1.label']), collapse = ' + ')))
face.5.classifier <- neuralnet(myform, training.set, hidden = 5, rep=100, linear.output = FALSE, threshold = 0.1)
summary(face.5.classifier)
```
Model for 5 hidden nodes
```{r}
class.index<-length(test.set)
face.prediction<-compute(face.5.classifier,test.set[,-class.index])
face.prediction$net.result
```
Prediction for 5 hidden nodes
```{r}
classifications<-ifelse(face.prediction$net.result>0.5,1,-1)
classifications
```
Classification for 5 hidden nodes
```{r}
table(test.set[,class.index],classifications)
```
Classification accuracy table for 5 hidden nodes

```{r}
library(neuralnet)
myform <- as.formula(paste('class1.label ~ ',paste(names(training.set[!names(training.set) %in% 'class1.label']), collapse = ' + ')))
face.7.classifier <- neuralnet(myform, training.set, hidden = 7, rep=100, linear.output = FALSE, threshold = 0.1)
summary(face.7.classifier)
```
Model for 7 hidden nodes
```{r}
class.index<-length(test.set)
face.prediction<-compute(face.7.classifier,test.set[,-class.index])
face.prediction$net.result
```
Prediction for 7 hidden nodes
```{r}
classifications<-ifelse(face.prediction$net.result>0.5,1,-1)
classifications
```
Classification for 7 hidden nodes
```{r}
table(test.set[,class.index],classifications)
```
Classification accuracy table for 7 hidden nodes

```{r}
library(neuralnet)
myform <- as.formula(paste('class1.label ~ ',paste(names(training.set[!names(training.set) %in% 'class1.label']), collapse = ' + ')))
face.9.classifier <- neuralnet(myform, training.set, hidden = 9, rep=100, linear.output = FALSE, threshold = 0.1)
summary(face.9.classifier)
```
Model for 9 hidden nodes
```{r}
class.index<-length(test.set)
face.prediction<-compute(face.9.classifier,test.set[,-class.index])
face.prediction$net.result
```
Prediction for 9 hidden nodes
```{r}
classifications<-ifelse(face.prediction$net.result>0.5,1,-1)
classifications
```
Classification for 9 hidden nodes
```{r}
table(test.set[,class.index],classifications)
```
Classification accuracy table for 9 hidden nodes

```{r}
library(neuralnet)
myform <- as.formula(paste('class1.label ~ ',paste(names(training.set[!names(training.set) %in% 'class1.label']), collapse = ' + ')))
face.11.classifier <- neuralnet(myform, training.set, hidden = 11, rep=100, linear.output = FALSE, threshold = 0.1)
summary(face.11.classifier)
```
Model for 11 hidden nodes
```{r}
class.index<-length(test.set)
face.prediction<-compute(face.11.classifier,test.set[,-class.index])
face.prediction$net.result
```
Prediction for 11 hidden nodes
```{r}
classifications<-ifelse(face.prediction$net.result>0.5,1,-1)
classifications
```
Classification for 11 hidden nodes
```{r}
table(test.set[,class.index],classifications)
```
Classification accuracy table for 11 hidden nodes
